### Question 20
#### a) $\mu = \int_{-4}^2 log(x+5)\, dx = 7log7 - 6 \approx 7.6214$
We want to make a transformation where $t = \frac{x+4}6$, then $x = 6t-4$, $dx = 6dt$. 
So the new integral is $\mu = 6\int_0^1 log(6t+1)\, dt$
```{r}
set.seed(271)
t = runif(1000)
int = log(6*t+1) *6
mean = mean(int) # estimated value
variance = var(int)/sqrt(1000) #sample variance
mean
c(mean-1.96*variance,mean+1.96*variance) # Confidence Interval
```

#### b) $\mu = \int_{-\infty}^{\infty} exp(-x^2/2)\ dx = \sqrt{2\pi} \approx 2.50663$
$\mu = \int_{-\infty}^{\infty} exp(-x^2/2)\ dx = 2\int_0^{\infty} exp(-x^2/2)\ dx$ as $x^2$ is an even function. We take $t = exp(-x)$, then $x = -\ln{t}$, $dx = -\frac{1}t\ dt$.
```{r}
t = runif(1000)
int = 2*exp(-log(t)^2/2)/t
mean = mean(int) #estimated value
mean
variance = var(int)/sqrt(1000) # sample variance
c(mean-1.96*variance,mean+1.96*variance) # Confidence Interval
```

### Question 21
#### a)
```{r}
set.seed(271)
n = 1000000
u = runif(n)
cor(u,sqrt(1-u^2)) # it is quite negatively related
```

#### b)
```{r}
u = runif(n)
su = u^2
cor(su,sqrt(1-su))
```

Comparing the two results, we see that both number are negative, and the second number is smaller, showing a stronger negative correlation. As indicated in the way of coding, the first case is about u and $\sqrt{u}$, with some transformation, while the second case is both about u^2 in different functions. Therefore the second case should indicates a stronger correlation.

### Question 22
#### a) $\mu = \int_0^1 exp(-x^2)\, dx$, using antithetic method
```{r}
set.seed(271)
n = 1000
## cmc
x = runif(n)
g = exp(-x^2)
meang = mean(g)
varcmc = var(g)/n
### antithetic
u = runif(n/2)
v = 1-u
h = (exp(-u^2)+exp(-v^2))/2
meanh = mean(h)
varanti = 2*var(h)/n
meang
meanh
varcmc/varanti #efficiency
```
Therefore in order to have the same level of accuracy as 1000 anti samples, cmc needs 269492 samples.

#### b) $\mu = \int_0^1 log(1+x)\, dx$, using control variance with $h(x)=\sqrt{x}$
For control variance with h(x), now we have $\mu = \int_0^1 \log(1+x)-\sqrt{x}\, dx + \int_0^1 \sqrt{x}\,dx = \int_0^1 \log(1+x)-\sqrt{x}\, dx + \frac{2}3 $. We use cmc to estimate the first part.
```{r}
## cmc
x = runif(n)
g = log(1+x)
meang = mean(g)
varcmc = var(g)/n
## control variance
u = runif(n)
v = log(1+u)
w = sqrt(u)
y = v-w
meancv = mean(y) +2/3
varcv = var(y)/n
meang
meancv
varcmc/varcv
```
Therefore in order to get the same level of accracy as cmc using control variance we need 1/19.34066 the number of function evaluations.

#### c)  $\mu = \int_0^1 log(1+x)\, dx$, using optimal control with $h(x)=\sqrt{x}$
For optimal control variance with h(x), we have $\mu = \int_0^1 \log(1+x)-k\sqrt{x}\, dx + k\int_0^1 \sqrt{x}\,dx$, where k is a constant that minimizes the variance.
```{r}
## cmc
x = runif(n)
g = log(1+x)
meang = mean(g)
varcmc = var(g)/n
## control variance
u = runif(n)
v = log(1+u)
w = sqrt(u)
c = cov(v,w)
k = c/var(w)
y = v-k*w
meancv = mean(y)+k*2/3
varcv = (var(v)+var(w)*k^2-2*k*c)/n
meang
meancv
varcmc/varcv
```
To get the same level of accuracy as optimal control variance in this case, cmc needs 82,922 sample function evaluations.

#### e) importance sampling
Similar to 20 b), we use the same transformation for cmc.
```{r}
## cmc
t = runif(1000)
g = sqrt(2/pi)*exp(-log(t)^2/2)/t
mean = mean(g)
## importance sampling
u = runif(n)
x = -log(u)
h = sqrt(2/pi)*exp(-x^2/2)/exp(-x)
output = mean(h)
meang
output

```

