---
title: "a4q3"
output:
  html_document: default
  pdf_document:
    fig_height: 4
    fig_width: 4
---
## Question 3
### Part a
```{r,fig.height=4,fig.width=4}
library("tseries",quietly=T)
rim<-get.hist.quote(instrument="rim",quote="Close")
par(mfcol=c(1,1))
plot(rim,xlab="Time",ylab="Stock Price",main="RIM Stock Price from 2002 to 2014")
```

Comment: The stock price does not have a constant mean and variance over the time. It variates a lot by the time t, and the stock price looks quite dependent on the previous values in some sense. We can consider some specific trends for a period of time, for example logistic regression from 2009 to 2012.

### Part b
```{r,fig.height=4,fig.width=4}
rim<-get.hist.quote(instrument="rim",quote="Close",start="2010-03-17",end="2015-03-16")
returns<-log(rim/lag(rim,h=-1))
```
We have created a new time series of the log stock returns, $i.e. X_t = log(Y_t/Y_{t-1}) = log(Y_t)-log(Y_{t-1})$.

### Part c
```{r,fig.height=4,fig.width=4}
plot(returns,xlab="Time",ylab="log stock return",main="RIM Stock Return from 2010 to 2015")
```

Comment: The stock returns look random with constant mean(0) but the variance is different over time.

### Part d
```{r,fig.height=9,fig.width=6}
par(mfcol=c(3,1))
returns<-as.numeric(returns)
acf(returns)
acf(returns^2,main="Series Square of Returns")
acf(abs(returns),main="Series Absolute Value of Returns")
```

Comment: There is a little negative spike on lag=1 for the acf graph. There are several spikes on the square of return and absolute value of return ACF plots. Therefore considering a ARCH/GARCH model would be appropriate.



Comment: The residual looks random with zero mean and constant variance. However the Q-Q plot has quite heavy tails and the plot is not like a straight line. 

### Part f
```{r}
returns.garch <- garch(returns, order=c(1,1), trace=F)
summary(returns.garch)
plot(returns.garch$residuals,type="l")
qqnorm(returns.garch$residuals)
qqline(returns.garch$residuals)
```


### Part g
```{r}
library(fGarch,quietly=T)
nfit = garchFit(returns=~arma(0,1)+garch(1,1),trace=F)
nfit
```
